Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-23 paper/sec-analysis.tex
more work on paper

>>>>

In addition, trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to all large-$R$ jets in the event.
The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$~\cite{Ellis:1993tq} 
subjets with $R_{\textrm{sub}} = 0.2$.
Subjets with tranverse momentum less than 5\% of the tranverse momentum of the large-$R$ jet are removed.
The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass, which is particularly susceptible
to soft, wide-angle contaminations. This is illustrated in Fig.~\ref{fig:m_H_PU_MitiCompare}. The mass distributions for jets to which no trimming
is applied (red) peaks at around 160~GeV (after PU subtraction with {\tt SoftKiller}). If trimming is applied in addition to {\tt SoftKiller}, 
the distributions (green) peak close to the Higgs mass of 125~GeV. For comparison, the distributions for trimmed jets are shown for events 
in which {\tt SoftKiller} is not applied (blue).

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \includegraphics[width=0.49\textwidth]{plots/histo_m_H0_boost.pdf}
      \includegraphics[width=0.49\textwidth]{plots/histo_m_H1_boost.pdf}
  \caption{\small
    Comparison of the invariant mass distributions of the leading (left)
    and subleading (right) Higgs candidates in the boosted category.
    The distributions are shown for the cases without PU, and with
    PU, $\la n_{PU}\ra=80$, and applying either only {\tt SoftKiller},
    or only trimming, or both {\tt SoftKiller} and trimming.
}
\label{fig:m_H_PU_MitiCompare}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-23 paper/sec-conclusions.tex
more work on paper

>>>>

Efficiently triggering on the $4b$ final state provides a large experimental challenge.
%
In order to reduce the rate from background QCD processes sufficiently,
to access these $p_T$ regimes, (multi-)jet triggers
using $b$-quark tagging information online for one or more jets are likely to be important.
%
The additional rejection provided by this could enable events to be selected efficiently, with four jets down to $p_T=45$ GeV in the resolved category,
and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
$p_T=200$ GeV.
